Versatile Robust Clustering of Ad Hoc Cognitive Radio Network

### 2016-03-29 journal-draft/bare_jrnl_comsoc.tex
minor changes

\begin{table}[h!]
\caption{Notations in robust clustering problem}
\label{tab1}
\centering
\begin{tabular}{llr}
\toprule
%\multicolumn{2}{c}{Item} \\
%\cmidrule(r){1-2}
Symbol & Description \\
\midrule
$\mathcal{N}$  & collection of secondary users\\
%$k_i$ & the working channel of user $i$\\
$\text{Nb}(i)$ & the neighborhood of CR node $i$    \\
$C(i)$ & a cluster whose cluster head is $i$  \\
%$k_i$   & set of available channels at CR node $i$  \\
$K_i$   & the set of available channels at CR node $i$  \\
$K(C(i))$   & the set of available CCCs of cluster $C(i)$ \\
%$h(C)$ & cluster head of a cluster $C$\\
$h_C$ & the cluster head of a cluster $C$\\
%$\text{CH}$ & cluster head\\
$\delta$ & desired cluster size\\
$S_i$ & a set of claiming clusters, each of which includes \\
& debatable node $i$ after phase I\\
$d_i$  & individual connectivity degree of CR node $i$\\
$g_i$  & social connectivity degree of CR node $i$\\
$C_i$  & the $i$th legitimate cluster (only appear in Sec.~\ref{centralized_opt})\\
\bottomrule
\end{tabular}
\end{table}

@@

After receiving the notification from a cluster head, a CR node, \eg $i$, is aware that it becomes one member of a cluster, then $i$ sets its individual connectivity degree to zero. %, which is smaller than all the possible individual connectivity degrees in the CR network.
Then node $i$ broadcasts its new individual connectivity degree to all its neighbours. 
%wrong:
%Note that there is no cluster head which receives the notification on cluster head eligibility, and there is a Lemma on this.
%\begin{theorem}{lemma}
%There is no cluster head receiving the notification message on cluster head eligibility, which is sent from a node which newly becomes a cluster head.
%\end{theorem}
%\begin{proof}
%We use contradiction to prove. 
%Assume a CR node $j$ is cluster head, and receives a notification on cluster head eligibility form CR node $i$. 
%According to the assumption on the reciprocal communication link, $i$ should have received the notification message from $j$ when $j$ becomes cluster head.
%Then CR node $i$ will set its individual connectivity degree to zero, and has no possibility to become a cluster head.
%\end{proof}
When a CR node $i$ is associated to multiple clusters, \ie $i$ has received multiple notifications of cluster head eligibility from different CR nodes, $d_i$ is still set to zero.
We manipulate the individual connectivity degree of the CR nodes, so that the nodes which locate outside of the a formed cluster can possibly become cluster heads, or be included into other clusters.
%Then every CR node becomes either cluster head or one member of at least one cluster.
%In other words, with this manipulation on its individual connectivity degree, every CR node in the network will be involved in the clustering process, the proof will be given later.
%Every CR user is involved in the clustering process and becomes either cluster head or member is described in theorem~\ref{clustering:theorem}.
We have the following theorem to show that as long as a secondary user's individual connectivity degree is not zero, that secondary user will be integrated into a certain cluster, or become a cluster head.
\begin{theorem}
\label{clustering:theorem}
Given a CRN, every secondary user is included into at least one cluster within $N$ steps.
\end{theorem}
Here, \textit{Step} means a secondary user conducts Algorithm~\ref{clustering:theorem} once.
The Proof is in Appendix~\ref{proof_clustering:theorem}.
According to Theorem~\ref{clustering:theorem}, we can assign reasonable amount of time for phase I to complete.

@@

\subsubsection{Guarantee Availability of Common Control Channel}
%After deciding itself being cluster head, CR node broadcasts to notify its neighbours on the dedicated control channel, meanwhile, $i$'s initial cluster is formed immediately, which is $i$'s neighbourhood except for those nodes which have become cluster heads, \ie $C_i=(\text{Nb}_i\setminus \text{CHs})\cup i$.
After executing phase I of ROSS, there are some secondary users which become cluster heads.
The cluster head and its neighbourhood (except for the CHs) become a cluster.
It is possible that there is no CCCs for some formed clusters, and we solve this problem with the following method.

@@

Given a cognitive radio network $\mathcal{N}$ where nodes are indexed from 1 to $N$ sequentially.
Based on certain correlation, certain secondary users constitute one cluster $C$.
$1\leq |C| \leqslant k$ where $|C|$ is the size of cluster $C$ and $k$ is a positive integer.
We name the collection of such clusters as $\mathcal{S}=\{C_1, C_2,\ldots,C_{|\mathcal{S}|}\}$ (the subscript $i$ is the unique index of cluster in $\mathcal{S}$, not the ID of cluster head of that cluster), $\mathcal{S}$ satisfies the following properties: $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = N$ and $K_{C_i}\neq \emptyset$ for any $i$ which satisfies $1\leq i \leq |\mathcal{S}|$.

We give a new definition of the number of CCCs, which distinguishes the centralized clustering problem discussed in this paper.
In this problem, the number of common control channels is $|K(C)|$ if $|C|>1$, and is zero when $|C|=1$.
We use $f(C)$ to denote this new definition of the number of CCCs of a cluster $C$.
The question of centralized clustering problem is to find a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, so that $\bigcup_{C_j\in \mathcal{S}'} C_j = N$, and $C_{j'}\cap C_j =\emptyset$ for $C_{j'}, C_j\in \mathcal{S}'$ and $j'\neq j$, so that $\sum_{C\in \mathcal{S}'} f$ is maximized.
% when $|C|>1$, and $f(\cdot)=0$ when $|C|=1$.
%As to $f(\cdot):z\rightarrow z$, under this problem setting, if only number of common channels are given consideration, only singleton clusters will be preferred, which contradicts to our goal of clustering CR nodes together, thus we choose $f(\cdot)= |K_{C}|\cdot |C|$, the product of number of common channels and cluster size.
The decision version of centralized clustering in CRN is to ask whether there exists no-empty $\mathcal{S}'\subseteq \mathcal{S}$, so that $\sum_{C\in \mathcal{S}'} f \geqslant \lambda$ where $\lambda$ is a real number.% in stead of to maximize $\sum_{C\in \mathcal{S}'} f$.
\end{mydef}

>>>>

\begin{table}[h!]
\caption{Notations in robust clustering problem}
\label{tab1}
\centering
\begin{tabular}{llr}
\toprule
%\multicolumn{2}{c}{Item} \\
%\cmidrule(r){1-2}
Symbol & Description \\
\midrule
$\mathcal{N}$  & collection of secondary users\\
$k(i)$ & the working channel of user $i$\\
$\text{Nb}(i)$ & the neighborhood of CR node $i$    \\
$C(i)$ & a cluster whose cluster head is $i$  \\
%$k_i$   & set of available channels at CR node $i$  \\
$K_i$   & the set of available channels at CR node $i$  \\
$K(C(i))$   & the set of available CCCs of cluster $C(i)$ \\
%$h(C)$ & cluster head of a cluster $C$\\
$h_C$ & the cluster head of a cluster $C$\\
%$\text{CH}$ & cluster head\\
$\delta$ & desired cluster size\\
$S_i$ & a set of claiming clusters, each of which includes \\
& debatable node $i$ after phase I\\
$d_i$  & individual connectivity degree of CR node $i$\\
$g_i$  & social connectivity degree of CR node $i$\\
$C_i$  & the $i$th legitimate cluster (only appear in Sec.~\ref{centralized_opt})\\
\bottomrule
\end{tabular}
\end{table}

@@

After receiving the notification from a cluster head, a CR node, \eg $i$, is aware that it becomes one member of a cluster, then $i$ sets its individual connectivity degree to zero. %, which is smaller than all the possible individual connectivity degrees in the CR network.
Then node $i$ broadcasts its new individual connectivity degree to all its neighbours. 
%wrong:
%Note that there is no cluster head which receives the notification on cluster head eligibility, and there is a Lemma on this.
%\begin{theorem}{lemma}
%There is no cluster head receiving the notification message on cluster head eligibility, which is sent from a node which newly becomes a cluster head.
%\end{theorem}
%\begin{proof}
%We use contradiction to prove. 
%Assume a CR node $j$ is cluster head, and receives a notification on cluster head eligibility form CR node $i$. 
%According to the assumption on the reciprocal communication link, $i$ should have received the notification message from $j$ when $j$ becomes cluster head.
%Then CR node $i$ will set its individual connectivity degree to zero, and has no possibility to become a cluster head.
%\end{proof}
When a CR node $i$ is associated to multiple clusters, \ie $i$ has received multiple notifications of cluster head eligibility from different CR nodes, $d_i$ is still set to zero.
We manipulate the individual connectivity degree of the CR nodes, so that the nodes which locate outside of the a formed cluster can possibly become cluster heads, or be included into other clusters.
%Then every CR node becomes either cluster head or one member of at least one cluster.
%In other words, with this manipulation on its individual connectivity degree, every CR node in the network will be involved in the clustering process, the proof will be given later.
%Every CR user is involved in the clustering process and becomes either cluster head or member is described in theorem~\ref{clustering:theorem}.
We have the following theorem to show that as long as a secondary user's individual connectivity degree is not zero, that secondary user will be integrated into a certain cluster, or become a cluster head.
\begin{theorem}
\label{clustering:theorem}
Given a CRN, every secondary user is included into at least one cluster within $N$ steps.
\end{theorem}
Here, \textit{Step} means one secondary user conducts Algorithm~\ref{clustering:theorem} once.
The Proof is in Appendix~\ref{proof_clustering:theorem}.
According to Theorem~\ref{clustering:theorem}, we can assign reasonable amount of time for phase I to complete.

@@

\subsubsection{Guarantee the Availability of Common Control Channel}
%After deciding itself being cluster head, CR node broadcasts to notify its neighbours on the dedicated control channel, meanwhile, $i$'s initial cluster is formed immediately, which is $i$'s neighbourhood except for those nodes which have become cluster heads, \ie $C_i=(\text{Nb}_i\setminus \text{CHs})\cup i$.
After executing phase I of ROSS, there are some secondary users which become cluster heads.
The cluster head and its neighbourhood (except for the CHs) become a cluster.
It is possible that there is no CCCs for some formed clusters, and we solve this problem with the following method.

@@

Given a cognitive radio network $\mathcal{N}$ where nodes are indexed from 1 to $N$ sequentially.
Based on certain correlation, certain secondary users constitute one cluster $C$.
$1\leq |C| \leqslant k$ where $|C|$ is the size of cluster $C$ and $k$ is a positive integer.
We name the collection of such clusters as $\mathcal{S}=\{C_1, C_2,\ldots,C_{|\mathcal{S}|}\}$, where $\mathcal{S}$ satisfies the following properties: $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = N$ and $K(C(i))\neq \emptyset$ for any $i$ which satisfies $1\leq i \leq |\mathcal{S}|$.

%, which distinguishes the centralized clustering problem discussed in this paper.
We give a new definition of the number of CCCs, where the number of common control channels is $|K(C)|$ if $|C|>1$, and is zero when $|C|=1$.
We use $f(C)$ to denote the number of CCCs of a cluster $C$ in the new definition.

The centralized clustering problem is to find a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, so that $\bigcup_{C_j\in \mathcal{S}'} C_j = N$, and $C_{j'}\cap C_j =\emptyset$ for $C_{j'}, C_j\in \mathcal{S}'$ and $j'\neq j$, so that $\sum_{C\in \mathcal{S}'} f(C)$ is maximized.
% when $|C|>1$, and $f(\cdot)=0$ when $|C|=1$.
%As to $f(\cdot):z\rightarrow z$, under this problem setting, if only number of common channels are given consideration, only singleton clusters will be preferred, which contradicts to our goal of clustering CR nodes together, thus we choose $f(\cdot)= |K_{C}|\cdot |C|$, the product of number of common channels and cluster size.
The decision version of centralized clustering in CRN is to ask whether there exists a no-empty $\mathcal{S}'\subseteq \mathcal{S}$, so that $\sum_{C\in \mathcal{S}'} f \geqslant \lambda$ where $\lambda$ is a real number.% in stead of to maximize $\sum_{C\in \mathcal{S}'} f$.
\end{mydef}
